---
title: "simulation results for RSCA (DISCOsca, pca_gca, VAF)"
author: "Zhengguo Gu"
date: "1 februari 2017"
output: html_document
---

#Install the packages (ingore this once the package is published on CRAN)

First download the package "RSCA_0.1.1.tar.gz" then run the following line\
*install.packages(pkg="RSCA_0.1.1.tar.gz", repos = NULL)*\
(It seems that the package needs to be downloaded to C:/Users/.../Documents.) The following function shows which functions are included in the SCA package. We are going to test all the functions. 
```{r}
help(package=RSCA)
```

# situation 1: 1 common component (no sparseness) and 4 distinctive components, 2 blocks
1 0 0 1 1\
1 1 1 0 0\
```{r}
set.seed(112)

I <- 28
J1 <- 144
J2 <-44
Jk <- c(J1, J2)
sumJk <- sum(J1 + J2)
R <- 5
Comm <- 1

PropNoise <- 0.05
Perc0Com <- 0.9  


DATA1 <- matrix(rnorm(I*J1, mean = 0, sd = 1), I, J1)
DATA2 <- matrix(rnorm(I*J2, mean = 0, sd = 1), I, J2)
DATA <- cbind(DATA1, DATA2)

svddata <- svd(DATA, R, R)
Ttrue <- svddata$u
PTrueC <- as.matrix(svddata$v) %*% diag(svddata$d[1:R])   #note that only the first R eigen   values are needed.

PTrueCBlock1 <- PTrueC[1:J1,]
PTrueCBlock2 <- PTrueC[(J1+1):(J1+J2),]

v1 <- c(2, 3)
PTrueCBlock1[, v1] <- 0
v2 <- c(4, 5)
PTrueCBlock2[, v2] <- 0
dist <- c(v1, v2)

PTrueCnew <- rbind(PTrueCBlock1, PTrueCBlock2)

XTrue <- Ttrue %*% t(PTrueCnew)
SSXtrue <- sum(XTrue ^ 2)

Noise <- matrix(rnorm(I*(J1+J2), mean = 0, sd = 1), I, J1+J2)
SSNoise <- sum(Noise ^ 2)
g <- sqrt(PropNoise*SSXtrue/(SSNoise-PropNoise*SSNoise))
NoiseNew <- g*Noise
SSNoiseNew <- sum(NoiseNew ^ 2)
Xgenerate <- XTrue + NoiseNew
SSXgenerate <- sum(Xgenerate ^ 2)
NoiseVSgenerate <- SSNoiseNew/SSXgenerate
```
## use VAF to identify number of components
Given the data, we generally do not know how many components there are, thus, we can try a few numbers, say R=10.
```{r}
RSCA::VAF(Xgenerate, Jk, R=10)
```
The results suggest that R=5, which is correct.

## use DISCOsca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::DISCOsca(Xgenerate, R=5, Jk)
```
The results suggest that \
[1,]    1    1    1    1    1\
[2,]    0    0    1    0    0\
Note that DISCOsca relies on a special rule on P. 

## use pca_gca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::pca_gca(Xgenerate, Jk)
```
The results:
The number of components in each block are: 3 3\
There are in total 1 common components in the concatenated data.\
This means that in total there are 5 compnents, 1 of them is the common component, which is in line with the setup. 

#situation 2, 0 common componnet, 5 distinctive components, 2 blocks
2 blocks, 5 components: (note that this is with respect to the P matrix)\
0 0 0 1 1\
1 1 1 0 0\
```{r}  
set.seed(112)

I <- 28
J1 <- 144
J2 <-44
Jk <- c(J1, J2)
sumJk <- sum(J1 + J2)
R <- 5
Comm <- 1 #not used

PropNoise <- 0.05
Perc0 <- 0.3

NRSTARTS <- 20
Ndataset <- 50
MAXITER <- 400

DATA1 <- matrix(rnorm(I*J1, mean = 0, sd = 1), I, J1)
DATA2 <- matrix(rnorm(I*J2, mean = 0, sd = 1), I, J2)
DATA <- cbind(DATA1, DATA2)

svddata <- svd(DATA, R, R)
Ttrue <- svddata$u
PTrueC <- as.matrix(svddata$v) %*% diag(svddata$d[1:R])   #note that only the first R eigen values are needed.

PTrueCBlock1 <- PTrueC[1:J1,]
PTrueCBlock2 <- PTrueC[(J1+1):(J1+J2),]

v1 <- c(1, 2, 3)
PTrueCBlock1[, v1] <- 0
v2 <- c(4, 5)
PTrueCBlock2[, v2] <- 0

PTrueCnew <- rbind(PTrueCBlock1, PTrueCBlock2)
XTrue <- Ttrue %*% t(PTrueCnew)
SSXtrue <- sum(XTrue ^ 2)

Noise <- matrix(rnorm(I*(J1+J2), mean = 0, sd = 1), I, J1+J2)
SSNoise <- sum(Noise ^ 2)
g <- sqrt(PropNoise*SSXtrue/(SSNoise-PropNoise*SSNoise))
NoiseNew <- g*Noise
SSNoiseNew <- sum(NoiseNew ^ 2)
Xgenerate <- XTrue + NoiseNew
SSXgenerate <- sum(Xgenerate ^ 2)
NoiseVSgenerate <- SSNoiseNew/SSXgenerate
```

## use VAF to identify number of components
Given the data, we generally do not know how many components there are, thus, we can try a few numbers, say R=10.
```{r}
RSCA::VAF(Xgenerate, Jk, R=10)
```
The results suggest that R=5, which is correct.

## use DISCOsca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::DISCOsca(Xgenerate, R=5, Jk)
```
The results suggest that\
[1,]    1    1    1    1    1\
[2,]    0    1    0    0    0

## use pca_gca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::pca_gca(Xgenerate, Jk)
```
The number of components in each block are: 2 3\
There are in total 0 common components in the concatenated data.\

# situation 3, 1 common components, 2 distinctive components, 3 blocks
3 blocks, 3 components:\
1 1 0\
1 0 1\
1 1 0\

```{r}
set.seed(112)

I <- 28
J1 <- 44
J2 <-44
J3 <- 44
Jk <- c(J1, J2, J3)
sumJk <- sum(J1 + J2 + J3)
R <- 3
Comm <- 1

PropNoise <- 0.05
Perc0 <- 0.3

DATA1 <- matrix(rnorm(I*J1, mean = 0, sd = 1), I, J1)
DATA2 <- matrix(rnorm(I*J2, mean = 0, sd = 1), I, J2)
DATA3 <- matrix(rnorm(I*J2, mean = 0, sd = 1), I, J3)
DATA <- cbind(DATA1, DATA2, DATA3)

svddata <- svd(DATA, R, R)
Ttrue <- svddata$u
PTrueC <- as.matrix(svddata$v) %*% diag(svddata$d[1:R])   #note that only the first R eigen values are needed.

PTrueCBlock1 <- PTrueC[1:J1,]
PTrueCBlock2 <- PTrueC[(J1+1):(J1+J2),]
PTrueCBlock3 <- PTrueC[(J1+J2+1):(J1+J2+J3),]

# 3 blocks, 3 components:
# 1 1 0
# 1 0 1
# 1 1 0
PTrueCBlock1[, 3] <- 0
PTrueCBlock2[, 2] <- 0
PTrueCBlock3[, 3] <- 0
PTrueCnew <- rbind(PTrueCBlock1, PTrueCBlock2, PTrueCBlock3)

XTrue <- Ttrue %*% t(PTrueCnew)
SSXtrue <- sum(XTrue ^ 2)

Noise <- matrix(rnorm(I*(J1+J2+J3), mean = 0, sd = 1), I, J1+J2+J3)
SSNoise <- sum(Noise ^ 2)
g <- sqrt(PropNoise*SSXtrue/(SSNoise-PropNoise*SSNoise))
NoiseNew <- g*Noise
SSNoiseNew <- sum(NoiseNew ^ 2)
Xgenerate <- XTrue + NoiseNew
SSXgenerate <- sum(Xgenerate ^ 2)
NoiseVSgenerate <- SSNoiseNew/SSXgenerate
```
## use VAF to identify number of components
Given the data, we generally do not know how many components there are, thus, we can try a few numbers, say R=10.
```{r}
RSCA::VAF(Xgenerate, Jk, R=10)
```
The results suggest that R=3, which is correct.

## use DISCOsca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::DISCOsca(Xgenerate, R=3, Jk)
```
The results suggest \
[1,]    1    1    1 \
[2,]    1    0    1 \
[3,]    0    1    0 

## use pca_gca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::pca_gca(Xgenerate, Jk)
```
The results are as follows
The number of components in each block are: 2 2 2
There are in total 0 common components in the concatenated data. 
The results are NOT in line  with the setup. 


# situation 4, 1 common components, 4 distinctive components, 3 blocks
3 blocks, 5 components:\
1 1 0 0 1\
1 0 1 1 0\
1 1 0 1 1\

```{r}
set.seed(112)

I <- 28
J1 <- 44
J2 <-44
J3 <- 44
Jk <- c(J1, J2, J3)
sumJk <- sum(J1 + J2 + J3)
R <- 5
Comm <- 1

PropNoise <- 0.05
Perc0 <- 0.3

DATA1 <- matrix(rnorm(I*J1, mean = 0, sd = 1), I, J1)
DATA2 <- matrix(rnorm(I*J2, mean = 0, sd = 1), I, J2)
DATA3 <- matrix(rnorm(I*J2, mean = 0, sd = 1), I, J3)
DATA <- cbind(DATA1, DATA2, DATA3)

svddata <- svd(DATA, R, R)
Ttrue <- svddata$u
PTrueC <- as.matrix(svddata$v) %*% diag(svddata$d[1:R])   #note that only the first R eigen values are needed.

PTrueCBlock1 <- PTrueC[1:J1,]
PTrueCBlock2 <- PTrueC[(J1+1):(J1+J2),]
PTrueCBlock3 <- PTrueC[(J1+J2+1):(J1+J2+J3),]

#3 blocks, 5 components:\
#1 1 0 0 1\
#1 0 1 1 0\
#1 1 0 1 1\
PTrueCBlock1[, c(3, 4)] <- 0
PTrueCBlock2[, c(2, 5)] <- 0
PTrueCBlock3[, 3] <- 0
PTrueCnew <- rbind(PTrueCBlock1, PTrueCBlock2, PTrueCBlock3)

XTrue <- Ttrue %*% t(PTrueCnew)
SSXtrue <- sum(XTrue ^ 2)

Noise <- matrix(rnorm(I*(J1+J2+J3), mean = 0, sd = 1), I, J1+J2+J3)
SSNoise <- sum(Noise ^ 2)
g <- sqrt(PropNoise*SSXtrue/(SSNoise-PropNoise*SSNoise))
NoiseNew <- g*Noise
SSNoiseNew <- sum(NoiseNew ^ 2)
Xgenerate <- XTrue + NoiseNew
SSXgenerate <- sum(Xgenerate ^ 2)
NoiseVSgenerate <- SSNoiseNew/SSXgenerate
```
## use VAF to identify number of components
Given the data, we generally do not know how many components there are, thus, we can try a few numbers, say R=10.
```{r}
RSCA::VAF(Xgenerate, Jk, R=10)
```
The results suggest that R=5, which is correct.

## use DISCOsca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::DISCOsca(Xgenerate, R=5, Jk)
```
DISCOsca is skipped, because it takes too much time to run. 

## use pca_gca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::pca_gca(Xgenerate, Jk)
```
The number of components in each block are: 3 3 4
There are in total 1 common components in the concatenated data, which is correct. 

# situation 5, 2 common components, 3 distinctive components, 3 blocks
3 blocks, 5 components:\
1 1 0 0 1\
1 1 1 1 0\
1 1 0 1 1\

```{r}
set.seed(112)

I <- 28
J1 <- 44
J2 <-44
J3 <- 44
Jk <- c(J1, J2, J3)
sumJk <- sum(J1 + J2 + J3)
R <- 5
Comm <- 1

PropNoise <- 0.05
Perc0 <- 0.3

DATA1 <- matrix(rnorm(I*J1, mean = 0, sd = 1), I, J1)
DATA2 <- matrix(rnorm(I*J2, mean = 0, sd = 1), I, J2)
DATA3 <- matrix(rnorm(I*J2, mean = 0, sd = 1), I, J3)
DATA <- cbind(DATA1, DATA2, DATA3)

svddata <- svd(DATA, R, R)
Ttrue <- svddata$u
PTrueC <- as.matrix(svddata$v) %*% diag(svddata$d[1:R])   #note that only the first R eigen values are needed.

PTrueCBlock1 <- PTrueC[1:J1,]
PTrueCBlock2 <- PTrueC[(J1+1):(J1+J2),]
PTrueCBlock3 <- PTrueC[(J1+J2+1):(J1+J2+J3),]

#3 blocks, 5 components:\
#1 1 0 0 1\
#1 1 1 1 0\
#1 1 0 1 1\
PTrueCBlock1[, c(3, 4)] <- 0
PTrueCBlock2[, 5] <- 0
PTrueCBlock3[, 3] <- 0
PTrueCnew <- rbind(PTrueCBlock1, PTrueCBlock2, PTrueCBlock3)

XTrue <- Ttrue %*% t(PTrueCnew)
SSXtrue <- sum(XTrue ^ 2)

Noise <- matrix(rnorm(I*(J1+J2+J3), mean = 0, sd = 1), I, J1+J2+J3)
SSNoise <- sum(Noise ^ 2)
g <- sqrt(PropNoise*SSXtrue/(SSNoise-PropNoise*SSNoise))
NoiseNew <- g*Noise
SSNoiseNew <- sum(NoiseNew ^ 2)
Xgenerate <- XTrue + NoiseNew
SSXgenerate <- sum(Xgenerate ^ 2)
NoiseVSgenerate <- SSNoiseNew/SSXgenerate
```

## use VAF to identify number of components
Given the data, we generally do not know how many components there are, thus, we can try a few numbers, say R=10.
```{r}
RSCA::VAF(Xgenerate, Jk, R=10)
```
The results suggest that R=5, which is correct.

## use DISCOsca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::DISCOsca(Xgenerate, R=5, Jk)
```
DISCOsca is skipped, because it takes too much time to run. 

## use pca_gca to identify common distictive processes.
```{r, eval=FALSE}
results <- RSCA::pca_gca(Xgenerate, Jk)
```
The number of components in each block are: 3 4 4
There are in total 2 common components in the concatenated data, which is correct.
